An efficient composition of bidirectional programs by tupling and lazy updates

### 2020-02-19 paper/main.tex
rename

\author{{Kanae Tsushima\inst{1}\orcidID{0000-0002-3383-3389}} \and \break
  {Bach-Trong Nguyen\inst{1}\orcidID{0000-0002-6342-6020}} \and \break
  {Robert Gl\"{u}ck\inst{2}\orcidID{0000-0001-6990-3935}} \and
  {Zhenjiang Hu\inst{3}\orcidID{0000-0002-9034-205X}}}

>>>>

\author{{Kanae Tsushima\inst{1}\orcidID{0000-0002-3383-3389}} \and \break
  {Bach Nguyen Trong\inst{1}\orcidID{0000-0002-6342-6020}} \and \break
  {Robert Gl\"{u}ck\inst{2}\orcidID{0000-0001-6990-3935}} \and
  {Zhenjiang Hu\inst{3}\orcidID{0000-0002-9034-205X}}}
